In this report, two simulation suites have been considered. The two suites use
markedly different numerical techniques to simulate isolated disk galaxies
that were extracted from cosmological simulations. A17 and D15 also use
black hole accretion rates that scale differently with local density, black
hole mass, and other properties; despite this the accretion histories for
black holes in both the \fire{} and \hagn{} simulations follow very similar
patterns. This, along with other evidence that there is not space to discuss,
lead both papers to the conclusion that efficient stellar and supernovae
feedback quench the black holes until some critical density threshold is
reached.

It is concerning that in none of the original simulation suite of 40 zoom-in
simulations from the \fire{} project that there is no implementation of black
holes; it can be argued that due to the low masses of the halos
($M_{\rm halo} < 2 \times 10^{12}$ M$_\odot$) AGN would have little effect
\citep[see e.g.][and citations]{bower_breaking_2006} however the focus of
the \fire{} project is to implement as much \emph{realistic} physics as
possible. It is notable that they evolve individual stellar popualtions for
each individual star particle, and yet do not incude any black hole
prescription at all; even in A17 they do not include any AGN feedback, and just
consider the feeding rate of the black hole.

Another concerning aspect of both A17 and D15 is that both papers only consider
a single halo. Whilst they do run numerical convergence tests (in which A17
performs better than D15; see ยง\ref{sec:bhs}) this prevents any statistical
analysis of the data; both papers conclude that the feeding rate is dependent
on the stellar feedback (by running with and without stellar feedback `turned
on') however this coud equally be due to some particular property of the
initial conditions considered. The fact that both papers come to the same
conclusion is promising, but a more statistically motivated study would have
more merit.
